% !TEX root = thesis.tex
% ************************** Thesis Acknowledgements **************************

\begin{acknowledgements}      
I have been told the most important single factor in a research career is having the right people as your mentors and, through little doing of my own, I have been extraordinarily fortunate in the people I have had in this role. 

I would like to thank my former supervisor at the University of Bath (now Google), Dr.~Matthew Brown, for his accepting me into the scholarship that has supported my research, and nurturing the research questions that sparked a fruitful first year of my studies. I thank Dr.~Duncan Robertson for somewhat inadvertently continuing in this role, especially for the many discussions we had, in particular his critical analysis, and the resulting insights which are responsible for much of the work I published. I would like to thank Professor Roberto Cipolla for so generously accepting me into his lab at the University of Cambridge, and the support he has shown me ever since. I thank Dr.~Richard Turner, also at the University of Cambridge, for agreeing to be my advisor and his time in helping me proofread the first year report. I thank Bart Andrews
%and Dr.\ Ignas Budvytis for their 
for his time in proofreading this dissertation. Most of all I would like to thank Dr.~Antonio Criminisi at Microsoft Research Cambridge, for his unfailing support beyond the call of a supervisor throughout the course of this degree, and without whom I'm quite sure my PhD would not have been possible.

Much of this work would not have been completed without the collaboration and input of numerous other people I have not listed at Microsoft Research and the University of Cambridge, both of which have more than lived up to their reputations as world class research institutions, but more importantly are immensely friendly environments fostering lasting collaboration and friendships. I'm honoured to have been able to learn in both of these environments.
\pagebreak

This dissertation ties together a large body of work completed during my time in Cambridge at both of these institutions, and below I detail collaborators for each of the papers from which this work emanated.

\begin{description}
	\item[\Cref{background}] is based loosely on my contributions to the MSALT4 (Advanced Machine Learning) course report on training deep autoencoders using contemporary deep learning methods, in collaboration with Felix Stahlberg, Moquan Wan and Joseph Zammit.

	\item[\Cref{lowrankfilters}] presents work presented at the International Conference on Learning Representations (ICLR) 2016, in San Jose, Puerto Rico~\citep{Ioannou2016} in collaboration with Duncan Robertson, Jamie Shotton, Roberto Cipolla and Antonio Criminisi.

	\item[\Cref{deeproots}] presents work presented at the IEEE Conference for Computer Vision and Pattern Recognition (CVPR) 2017, in Honolulu, Hawaii~\citep{ioannou2016e} in collaboration with Duncan Robertson, Roberto Cipolla and Antonio Criminisi.
	
	\item[\Cref{conditionalnetworks}] is based on work published in a Microsoft Research Technical Report~\citep{Ioannou2015} as the result of a 9-month research project, from March--Dec.~2014, at Microsoft Research Cambridge in extensive collaboration with Duncan Robertson, Darko Zikic, Peter Kontschieder, Jamie Shotton, Matthew Brown and Antonio Criminisi. Many of the figures are reproduced here with permission of Antonio Criminisi.

	\item[\Cref{futurework}] is based on a research proposal I wrote for a recent fellowship application.
\end{description}
\end{acknowledgements}
